\documentclass{article}
\usepackage[a4paper, total={7in, 10.5in}]{geometry}
\usepackage{hyperref}
\usepackage{helvet}  % Arial font
\renewcommand{\familydefault}{\sfdefault}
\usepackage{enumitem}  % http://ctan.org/pkg/enumitem
\setlist[itemize]{noitemsep, topsep=0pt}
\pagestyle{empty}  % remove page number

\begin{document}

\begin{center}
    \textbf{\huge LIEW XIN YI} \\

    xinyi2503@gmail.com \textbar\
    +65 9339 2866 \textbar\
    \href{https://github.com/xyliew25}{GitHub} \textbar\
    \href{https://linkedin.com/in/xyliew}{LinkedIn} \\

    \emph{*Required to serve a 3-year bond under the MOE Tuition Grant.
    EP Eligibility Letter available.}
\end{center}

\section*{EDUCATION}
\vspace{-12pt}
\rule{\textwidth}{3pt}
\textbf{National University of Singapore (NUS)} \hfill \textbf{Aug 2020 - June 2024}
\begin{itemize}
    \item Bachelor of Computing (Honours) in Computer Science
    \item CAP: 4.41 / 5.0
\end{itemize}

\section*{EXPERIENCE}
\vspace{-12pt}
\rule{\textwidth}{3pt}
\textbf{Student Researcher (Explicit-Control Evaluator for Java), Source Academy, Singapore}
\hfill \textbf{Aug 2023 - Apr 2024}
\begin{itemize}
    \item Developed and integrated a Java program visualizer for
    an introductory programming course in collaboration with an NUS professor.
    \item Overcame conceptual and technical challenges despite initial lack of experience
    in the programming language subfield, continuously brainstormed and refined ideas
    to ensure robust and evocative system.
    \item Achieved 3rd place in category in the 24th NUS SoC Term Project Showcase.
\end{itemize}

% \noindent required TODO what causes indentation?
\noindent \textbf{Software Engineering Intern (TEAMMATES), NUS-OSS, Singapore}
\hfill \textbf{May 2022 - July 2022}
\begin{itemize}
    \item Extended existing Google accounts only authentication system with
    Firebase Authentication to support domain independent accounts,
    conducted cost-benefit analysis for different framework implementations.
    \item Contributed to the peer evaluation software of 125 KLoC codebase with bug fixes,
    feature enhancements, new features, and data migration after a one-week onboarding period.
\end{itemize}

\section*{TEAM PROJECTS}
\vspace{-12pt}
\rule{\textwidth}{3pt}
\textbf{Covid-19 Analysis on Twitter and Mastodon}
\hfill \textbf{Apr 2023 - June 2023}
\begin{itemize}
    \item Collaborated on a React application to analyze big data stored in CouchDB,
    deployed via Ansible on the UniMelb Research Cloud.
    \item Managed the frontend using D3 for dynamic data visualization.
\end{itemize}

\noindent \textbf{PeerPrep}
\hfill \textbf{Aug 2022 - Nov 2022}
\begin{itemize}
    \item Developed a technical interview preparation website using React.js, microservices,
    NGINX API gateway, and GitHub Actions for GCP CI/CD.
    \item Implemented real-time matching features using WebSocket and Redis.
\end{itemize}

\noindent \textbf{Redesigning Pick-Up Drop-Off Points and Digital Services for Autonomous Vehicles}
\hfill \textbf{Aug 2022 - Nov 2022}
\begin{itemize}
    \item Worked with Industrial Design and Psychology majors through
    all phases of product development, including user research and design.
    \item Created a high-fidelity Flask prototype and integrated IoT sensors for the
    digital service solution, frequent communication with team to avoid implementation gaps.
\end{itemize}

\noindent \textbf{TurtleBot3 Robotics Autonomous Navigation}
\hfill \textbf{Jan 2021 - Apr 2021}
\begin{itemize}
    \item Convinced team to adopt Breadth-First Search instead of conventional
    wall-following algorithm to find shortest path to next destination point
    in autonomous navigation, earning in an honourable mention.
    \item First time collaborating with an interdisciplinary Engineering team,
    overcoming initial communication challenges.
\end{itemize}

\section*{SKILLS}
\vspace{-12pt}
\rule{\textwidth}{3pt}
\begin{itemize}
    \item \textbf{Proficient:} HTML/CSS/JS, Java, C/C++, Python, React, SQL, Git/GitHub
    \item \textbf{Basic:} C\#, Go, Rust, Node.js, Angular, Docker
\end{itemize}

\section*{SIDE INTERESTS}
\vspace{-12pt}
\rule{\textwidth}{3pt}
\textbf{Member, NUS Students' Community Service Club}
\hfill \textbf{Dec 2023 - Present}
\begin{itemize}
    \item Volunteer activities include helping elderly residents with chores, chatting,
    and technical assistance.
\end{itemize}

\noindent \textbf{Active Performer and Productions Manager, NUS Piano Ensemble}
\hfill \textbf{Aug 2020 - Apr 2024}
\begin{itemize}
    \item Performed in various concerts, including flagship concert TOUCH at
    Esplanade Recital Studio.
    \item Served in EXCO for 2 years, managing logistics and concert backstage.
\end{itemize}

\end{document}
